Systematic Misestimation of Machine Learning Performance in Neuroimaging Studies of Depression

### 2021-05-05 ms.tex
add floating barrier for acronyms
added ORCID links

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hhline}
\usepackage{pgf}
\usepackage{subcaption}
\usepackage{siunitx}
\sisetup{group-separator = {,},group-minimum-digits=4}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{bm}
\newcommand*{\B}[1]{\ifmmode\bm{#1}\else\textbf{#1}\fi}
\usepackage{nicefrac,xfrac}
\usepackage[]{authblk}
\usepackage[format=hang]{caption}
\usepackage{multirow, bigdelim}
\usepackage{xcolor}
\usepackage[linkbordercolor={0.818 0.394 0.394},urlbordercolor={0.366 0.528 0.745},hidelinks]{hyperref}
\usepackage{placeins}
\usepackage{import}
\usepackage[printonlyused, nohyperlinks]{acronym}
\usepackage{csquotes}
\usepackage[super]{nth}
\usepackage{blindtext}
\usepackage{float}

@@

\author[$\;\;$1,2]{\href{https://orcid.org/0000-0001-5164-8227}{Claas Flint \thanks{indicates that the authors contributed equally to the work and should be regarded as first authors.}}}
\author[$*$ 3,5]{\href{https://orcid.org/0000-0002-3353-8566}{Micah Cearns}}
\author[1]{\href{https://orcid.org/0000-0003-4749-3298}{Nils Opel}}
\author[1]{\href{https://orcid.org/0000-0002-7018-4525}{Ronny Redlich}}
\author[1]{\href{https://orcid.org/0000-0001-6587-2617}{David M. A. Mehler}}
\author[1]{\href{https://orcid.org/0000-0001-7459-6634}{Daniel Emden}}
\author[1]{\href{https://orcid.org/0000-0002-6241-1492}{Nils R. Winter}}
\author[1]{Ramona Leenings}
\author[4,8]{\href{https://orcid.org/0000-0001-6363-2759}{Simon B. Eickhoff}}
\author[6]{\href{https://orcid.org/0000-0002-2514-2625}{Tilo Kircher}}
\author[6]{\href{https://orcid.org/0000-0002-0564-2497}{Axel Krug}}
\author[6]{\href{https://orcid.org/0000-0002-0749-7473}{Igor Nenadic}}
\author[1]{\href{https://orcid.org/0000-0002-2445-9778}{Volker Arolt}}
\author[3]{Scott Clark}
\author[3,5,7]{\href{https://orcid.org/0000-0001-6548-426X}{Bernhard T. Baune}}
\author[2]{\href{https://orcid.org/0000-0001-7678-9528}{Xiaoyi Jiang}}
\author[$\;\;\ddagger$1]{\href{https://orcid.org/0000-0002-0623-3759}{Udo Dannlowski \thanks{indicates that the authors contributed equally to the work and should be regarded as senior authors.}}}
\author[$\;\dagger$1]{\href{https://orcid.org/0000-0002-8929-4134}{Tim Hahn}}

@@

\renewcommand{\shorttitle}{Performance Misestimation in Neuroimaging Studies of Depression}
\hypersetup{
    pdftitle={Systematic Misestimation of Machine Learning Performance in Neuroimaging Studies of Depression},
    pdfauthor={
        Claas Flint,
        Micah Cearns,
        Nils Opel,
        Ronny Redlich,
        David M. A. Mehler,
        Daniel Emden,
        Nils R. Winter,
        Ramona Leenings,
        Simon B. Eickhoff,
        Tilo Kircher,
        Axel Krug,
        Igor Nenadic,
        Volker Arolt,
        Scott Clark,
        Bernhard T. Baune,
        Xiaoyi Jiang,
        Udo Dannlowski,
        Tim Hahn
    },
    pdfproducer={Claas Flint},
    pdfkeywords={machine learning, neuroimaging, major depression, misestimation, small sample size, clinical translation},
    colorlinks=false
}

@@

    %%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
    \newpage
    \appendix
    %\widetext

@@

    \setcounter{equation}{1}
    \setcounter{figure}{0}
    \setcounter{table}{0}
    \setcounter{page}{1}
    %\makeatletter
    \renewcommand\thefigure{\thesection.\arabic{figure}}
    \renewcommand\thetable{\thesection.\arabic{table}}

@@

>>>>

\usepackage[english]{babel}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hhline}
\usepackage{pgf}
\usepackage{subcaption}
\usepackage{siunitx}
\sisetup{group-separator = {,},group-minimum-digits=4}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{bm}
\newcommand*{\B}[1]{\ifmmode\bm{#1}\else\textbf{#1}\fi}
\usepackage{nicefrac,xfrac}
\usepackage[]{authblk}
\usepackage[format=hang]{caption}
\usepackage{multirow, bigdelim}
\usepackage{xcolor}
\usepackage{placeins}
\usepackage{import}
\usepackage[printonlyused, nohyperlinks]{acronym}
\usepackage{csquotes}
\usepackage[super]{nth}
\usepackage{blindtext}
\usepackage{float}
\usepackage{orcidlink}

@@

\author[$\;\;$1,2]{Claas Flint\,\orcidlink{0000-0001-5164-8227} \thanks{indicates that the authors contributed equally to the work and should be regarded as first authors.}}
\author[$*$ 3,5]{Micah Cearns\,\orcidlink{0000-0002-3353-8566}}
\author[1]{Nils Opel\,\orcidlink{0000-0003-4749-3298}}
\author[1]{Ronny Redlich\,\orcidlink{0000-0002-7018-4525}}
\author[1]{David M. A. Mehler\,\orcidlink{0000-0001-6587-2617}}
\author[1]{Daniel Emden\,\orcidlink{0000-0001-7459-6634}}
\author[1]{Nils R. Winter\,\orcidlink{0000-0002-6241-1492}}
\author[1]{Ramona Leenings}
\author[4,8]{Simon B. Eickhoff\,\orcidlink{0000-0001-6363-2759}}
\author[6]{Tilo Kircher\,\orcidlink{0000-0002-2514-2625}}
\author[6]{Axel Krug\,\orcidlink{0000-0002-0564-2497}}
\author[6]{Igor Nenadic\,\orcidlink{0000-0002-0749-7473}}
\author[1]{Volker Arolt\,\orcidlink{0000-0002-2445-9778}}
\author[3]{Scott Clark}
\author[3,5,7]{Bernhard T. Baune\,\orcidlink{0000-0001-6548-426X}}
\author[2]{Xiaoyi Jiang\,\orcidlink{0000-0001-7678-9528}}
\author[$\;\;\ddagger$1]{Udo Dannlowski\,\orcidlink{0000-0002-0623-3759} \thanks{indicates that the authors contributed equally to the work and should be regarded as senior authors.}}
\author[$\;\dagger$1]{Tim Hahn\,\orcidlink{0000-0002-8929-4134}}

@@

\renewcommand{\shorttitle}{Performance Misestimation in Neuroimaging Studies of Depression}
\hypersetup{
    pdftitle={Systematic Misestimation of Machine Learning Performance in Neuroimaging Studies of Depression},
    pdfauthor={
        Claas Flint,
        Micah Cearns,
        Nils Opel,
        Ronny Redlich,
        David M. A. Mehler,
        Daniel Emden,
        Nils R. Winter,
        Ramona Leenings,
        Simon B. Eickhoff,
        Tilo Kircher,
        Axel Krug,
        Igor Nenadic,
        Volker Arolt,
        Scott Clark,
        Bernhard T. Baune,
        Xiaoyi Jiang,
        Udo Dannlowski,
        Tim Hahn
    },
    pdfproducer={Claas Flint},
    pdfkeywords={machine learning, neuroimaging, major depression, misestimation, small sample size, clinical translation},
    colorlinks=false,
    linkbordercolor={0.818 0.394 0.394},
    urlbordercolor={0.366 0.528 0.745},
    hidelinks
}

@@

    %%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
    \newpage
    \appendix

@@

    \setcounter{equation}{1}
    \setcounter{figure}{0}
    \setcounter{table}{0}
    \setcounter{page}{1}
    \renewcommand\thefigure{\thesection.\arabic{figure}}
    \renewcommand\thetable{\thesection.\arabic{table}}

@@

    \FloatBarrier
